---
title: "BioAge"
output: html_document
date: "2024-05-29"
---


This file calculates the brain age for GMV at instance 2

# Read in Data and Source
```{r}
source("init.r")

bioage_df <- read.csv(paste0(root, "data/BioAge_all.csv"))


healthy_unhealthy <- read.csv(paste0(root, "data/Healthy_Unhealthy_Age.csv"))


```

# Remove Columns that have more than 30% missing
```{r}
skim(bioage_df)

# Calculate the threshold for missing values (30% of the total number of rows)
threshold <- 0.3 * nrow(bioage_df)

# Select columns that have fewer than the threshold number of missing values
bioage_df_filtered <- bioage_df %>%
  dplyr::select(where(~ sum(is.na(.)) <= threshold))

bioage_df_filtered_noNA <- bioage_df_filtered %>% filter(complete.cases(.))

```

# Find column names and make codebook
```{r}
colnames(bioage_df_filtered_noNA)

```

# Merge with healthy_unhealthy
```{r}
bioage_healthy <- merge(bioage_df_filtered_noNA, healthy_0, by = "eid")
bioage_unhealthy <- merge(bioage_df_filtered_noNA, unhealthy_0, by = "eid")

nrow(bioage_healthy) # 40757
nrow(bioage_unhealthy) # 119955

table(bioage_healthy$p31)
table(bioage_unhealthy$p31) # 119955
```


# Visualize ROIs
```{r}
# Function to create scatterplot with r value
create_scatterplot <- function(data, age_col, bbb_col) {
  correlation <- cor(data[[age_col]], data[[bbb_col]], use = "complete.obs")
  plot <- ggplot(data, aes_string(x = age_col, y = bbb_col)) +
    geom_point(alpha = 0.5) +
    geom_smooth(method = "lm", se = FALSE, color = "blue") +
    labs(title = paste("Scatterplot of", bbb_col, "vs", age_col),
         subtitle = paste("r =", round(correlation, 2)),
         x = "Chronological Age",
         y = bbb_col) +
    theme_minimal()
  return(plot)
}

bbb_cols <- bioage_healthy %>% dplyr::select(p4079_i0_a0:p30850_i0) %>% names()

# Create and display all scatterplots
scatterplots <- map(bbb_cols, ~ create_scatterplot(bioage_healthy, "p21003_i0", .x))
print(scatterplots)
```




# Train Test Split for Healthy and Define Train Control
```{r}
set.seed(18)
trainIndex <- createDataPartition(bioage_healthy$p21003_i0, p = 0.8, list = FALSE)
trainData <- bioage_healthy[trainIndex,]
testData <- bioage_healthy[-trainIndex,]



# Select only age and GMV columns
trainData <- trainData %>% dplyr::select(p21003_i0, p31, p4079_i0_a0:p30850_i0)
testData <- testData %>% dplyr::select(p21003_i0, p31, p4079_i0_a0:p30850_i0)

trainData <- na.omit(trainData)
testData <- na.omit(testData)

nrow(trainData) # 32607
nrow(testData) # 8150

range(trainData$p21022)

```

# Define Train Control and nested-cross validation
```{r}

# Define the grids for hyperparameter tuning
ridge_grid <- expand.grid(.lambda = seq(0, 0.1, by = 0.01))
svr_grid <- expand.grid(.C = 2^(-5:2), .sigma = 2^(-5:2))

# Register parallel backend
cl <- makePSOCKcluster(detectCores() - 1)  # Use one less core than available
registerDoParallel(cl)

# Define training control for inner and outer cross-validation with parallel processing
inner_train_control <- trainControl(method = "cv", number = 3, allowParallel = TRUE)
outer_train_control <- trainControl(method = "cv", number = 10, savePredictions = "final", allowParallel = TRUE)


nested_cv_bioage <- function(data, method, tuneGrid, inner_train_control, outer_train_control) {
  # Create a progress bar
  pb <- progress_bar$new(
    format = "  [:bar] :percent eta: :eta",
    total = 10,  # Number of outer folds
    width = 60
  )
  
  # Outer loop cross-validation
  outer_cv_results <- lapply(1:10, function(i) {
    print(i)
    # Update progress bar
    pb$tick()
    
    # Split the data into training and testing sets
    trainIndex <- createDataPartition(data$p21003_i0, p = 0.9, list = FALSE)
    trainData <- data[trainIndex, ]
    testData <- data[-trainIndex, ]
    
    # Select the desired range of columns and exclude p31
    selected_columns <- trainData %>%
      dplyr::select(p21003_i0, p4079_i0_a0:p30850_i0) %>%
      names()
    
    # Create the formula
    formula <- as.formula(paste("p21003_i0 ~", paste(selected_columns[-1], collapse = " + ")))
    
    # Inner loop cross-validation for hyperparameter tuning
    model <- caret::train(
      formula, data = trainData,
      method = method,
      trControl = inner_train_control,
      tuneGrid = tuneGrid,
      preProcess = c("center", "scale")
    )
    
    # Predict on the training set to fit the extended model
    trainData$predicted_bioage <- predict(model, newdata = trainData)
    
    # Fit the extended model (Formula 2) on the training set
    extended_model <- lm(predicted_bioage ~ p21003_i0 + I(p21003_i0^2) + p31 + p31:p21003_i0 + p31:I(p21003_i0^2), data = trainData)
    
    # Predict on the test set
    testData$predicted_bioage <- predict(model, newdata = testData)
    
    # Predict corrected brain age on the test set using the extended model
    testData$corrected_bioage <- predict(extended_model, newdata = testData)
    
    # Calculate the corrected brain age gap
    testData$corrected_bio_age_gap <- testData$corrected_bioage - testData$p21003_i0
    
    # Calculate performance metrics
    performance <- postResample(testData$corrected_bioage, testData$p21003_i0)
    
    # Store the best hyperparameters
    best_params <- model$bestTune
    
    return(list(performance = performance, best_params = best_params))
  })
  
  return(outer_cv_results)
}


# Aggregate results and store best hyperparameters
aggregate_results <- function(cv_results) {
  performance_metrics <- do.call(rbind, lapply(cv_results, function(x) x$performance))
  best_hyperparams <- do.call(rbind, lapply(cv_results, function(x) x$best_params))
  
  return(list(performance_metrics = performance_metrics, best_hyperparams = best_hyperparams))
}

```


# Model Implementations
## Ridge Regression
```{r}

# Perform nested cross-validation for Ridge Regression
set.seed(18)
ridge_nested_cv_bioage <- nested_cv_bioage(trainData, "ridge", ridge_grid, inner_train_control, outer_train_control)

# Aggregate results
ridge_aggregate_results_bioage <- aggregate_results(ridge_nested_cv_bioage)
ridge_aggregate_results_bioage

# Save the ridge_nested_cv and ridge_aggregate_results objects to an RData file
save(ridge_nested_cv_bioage, ridge_aggregate_results_bioage, 
     file = paste0(root,"data/ridge_nested_cv_results_bioage.RData"))
```


## Support Vector Regression (SVR)
NB: Takes a while to run
```{r}
set.seed(18)

svr_nested_cv_bioage <- nested_cv_bioage(trainData, "svmRadial", svr_grid, inner_train_control, outer_train_control)

# Aggregate results
svr_aggregate_results_bioage <- aggregate_results(svr_nested_cv_bioage)
svr_aggregate_results_bioage

# Save the ridge_nested_cv and ridge_aggregate_results objects to an RData file
save(svr_nested_cv_bioage, svr_aggregate_results_bioage, 
     file = paste0(root,"data/svr_nested_cv_results_bioage.RData"))
```


## Gaussian Process Regression (GPR)
```{r}

gpr_nested_cv <- nested_cv(trainData, "gaussprRadial", NULL, inner_train_control, outer_train_control)

# Print results
gpr_results <- aggregate_results(gpr_nested_cv)
print(gpr_results$performance_metrics)
print(gpr_results$best_hyperparams)


# Save the ridge_nested_cv and ridge_aggregate_results objects to an RData file
save(gpr_nested_cv, gpr_results, file = paste0(root,"data/gpr_nested_cv_results.RData"))

stopCluster(cl)
```



```{r}
load("/Users/hansoochang/Drexel/UKBiobank/data/ridge_nested_cv_results.RData")
load("/Users/hansoochang/Drexel/UKBiobank/data/svr_nested_cv_results.RData")
```











