---
title: "Brain_Calc"
output: html_document
date: "2024-05-22"
---

This file calculates the brain age for GMV at instance 2


# Read in Data and Source
```{r}
source("init.r")

gmv_1 <- read.csv(paste0(root, "data/gmv_1.csv"))
gmv_2 <- read.csv(paste0(root, "data/gmv_2.csv"))
subcort_gmv <- read.csv(paste0(root, "data/subcort_gmv_inst2.csv"))

gmv12 <- merge(gmv_1, gmv_2, by = "eid")

subcort_gmv <- subcort_gmv %>% dplyr::select(-p25013_i3) # missing too many

gmv_all <- merge(subcort_gmv, gmv12, by = "eid")

gmv_all_noNA <- gmv_all %>% filter(complete.cases(.))

# Remove columns ending with .y and rename columns ending with .x
gmv_all_noNA <- gmv_all_noNA %>%
  dplyr::select(-matches("\\.y$")) %>%
  rename_with(~ gsub("\\.x$", "", .), matches("\\.x$"))

nrow(gmv_all_noNA)

healthy_unhealthy <- read.csv(paste0(root, "data/Healthy_Unhealthy_final.csv"))


```


# Find column names and make codebook
```{r}
colnames(gmv_all_noNA)

```

Codebook:
eid - Participant ID
p21022 - Age at recruitment
p25023_i2 - Vol of accumbens (left)
p25024_i2 - Vol of accumbens (right)
p25021_i2 - Vol of amygdala (left)
p25022_i2 - Vol of amygdala (right)
p25013_i3 - Vol of caudate (left)
p25013_i2 - Vol of caudate (right)
p25014_i2 - Vol of hippocampus (left)
p25019_i2 - Vol of hippocampus (right)
p25020_i2 - Vol of pallidum (left)
p25017_i2 - Vol of pallidum (right)
p25018_i2 - Vol of putamen (left)
p25015_i2 - Vol of putamen (right)
p25016_i2 - Vol of thalamus (left)
p25011_i2 - Vol of thalamus (right)


# Visualize ROIs
```{r}
# Function to create scatterplot with r value
create_scatterplot <- function(data, age_col, gmv_col) {
  correlation <- cor(data[[age_col]], data[[gmv_col]], use = "complete.obs")
  plot <- ggplot(data, aes_string(x = age_col, y = gmv_col)) +
    geom_point(alpha = 0.5) +
    geom_smooth(method = "lm", se = FALSE, color = "blue") +
    labs(title = paste("Scatterplot of", gmv_col, "vs", age_col),
         subtitle = paste("r =", round(correlation, 2)),
         x = "Chronological Age",
         y = gmv_col) +
    theme_minimal()
  return(plot)
}

# Get all GMV columns (assuming they start with 'gmv')
gmv_cols <- gmv_all_noNA %>% dplyr::select(p25023_i2:p25920_i2) %>% names()

# Create and display all scatterplots
scatterplots <- map(gmv_cols, ~ create_scatterplot(gmv_all_noNA, "p21022", .x))
print(scatterplots)
```

Generally, GMV decreases with age


# Source Healthy and Unhealthy then merge with brain age
Get participants who have no cancers or non-cancers illnesses at instance 1
Source from HealthyUnhealthySplit.Rmd
```{r}
gmv_healthy <- merge(gmv_all_noNA, healthy_0, by = "eid")
gmv_unhealthy <- merge(gmv_all_noNA, unhealthy_0, by = "eid")

nrow(gmv_healthy) # 1602
nrow(gmv_unhealthy) # 3044
table(gmv_healthy$p31)
mean(gmv_healthy$p21022)
sd(gmv_healthy$p21022)
```


# Train Test Split for Healthy and Define Train Control
```{r}
set.seed(18)
trainIndex <- createDataPartition(gmv_healthy$p21022, p = 0.8, list = FALSE)
trainData <- gmv_healthy[trainIndex,]
testData <- gmv_healthy[-trainIndex,]


# Select only age and GMV columns
trainData <- trainData %>% dplyr::select(p31, p21022:p25920_i2)
testData <- testData %>% dplyr::select(p31, p21022:p25920_i2)

trainData <- na.omit(trainData)
testData <- na.omit(testData)

nrow(trainData) # 1283
nrow(testData) # 319


```

# Define Train Control and nested-cross validation
```{r}

# Define the grids for hyperparameter tuning
ridge_grid <- expand.grid(.lambda = seq(0, 0.1, by = 0.01))
svr_grid <- expand.grid(.C = 2^(-5:2), .sigma = 2^(-5:2))

# Register parallel backend
cl <- makePSOCKcluster(detectCores() - 1)  # Use one less core than available
registerDoParallel(cl)

# Define training control for inner and outer cross-validation with parallel processing
inner_train_control <- trainControl(method = "cv", number = 3, allowParallel = TRUE)
outer_train_control <- trainControl(method = "cv", number = 10, savePredictions = "final", allowParallel = TRUE)

nested_cv <- function(data, method, tuneGrid, inner_train_control, outer_train_control) {
  # Create a progress bar
  pb <- progress_bar$new(
    format = "  [:bar] :percent eta: :eta",
    total = 10,  # Number of outer folds
    width = 60
  )
  
  # Outer loop cross-validation
  outer_cv_results <- lapply(1:10, function(i) {
    print(i)
    # Update progress bar
    pb$tick()
    
    # Split the data into training and testing sets
    trainIndex <- createDataPartition(data$p21022, p = 0.9, list = FALSE)
    trainData <- data[trainIndex, ]
    testData <- data[-trainIndex, ]
    
    # Create formula excluding p31
    formula <- as.formula(paste("p21022 ~ . - p31"))
    
    # Inner loop cross-validation for hyperparameter tuning
    model <- caret::train(
      formula, data = trainData,
      method = method,
      trControl = inner_train_control,
      tuneGrid = tuneGrid,
      preProcess = c("center", "scale")
    )
    
    # Predict on the training set to fit the extended model
    trainData$predicted_brainage <- predict(model, newdata = trainData)
    
    # Fit the extended model (Formula 2) on the training set
    extended_model <- lm(predicted_brainage ~ p21022 + I(p21022^2) + p31 + p31:p21022 + p31:I(p21022^2), data = trainData)
    
    # Predict on the test set
    testData$predicted_brainage <- predict(model, newdata = testData)
    
    # Calculate the uncorrected brain age gap
    testData$uncorrected_brain_age_gap <- testData$predicted_brainage - testData$p21022
    
    # Predict corrected brain age on the test set using the extended model
    testData$corrected_brainage <- predict(extended_model, newdata = testData)
    
    # Calculate the corrected brain age gap
    testData$corrected_brain_age_gap <- testData$corrected_brainage - testData$p21022
    
    # Calculate performance metrics for predicted brainage
    performance_predicted <- postResample(testData$predicted_brainage, testData$p21022)
    
    # Calculate performance metrics for corrected brain age
    performance_corrected <- postResample(testData$corrected_brainage, testData$p21022)
    
    # Store the best hyperparameters
    best_params <- model$bestTune
    
    # Save test data with added columns
    saved_test_data <- testData
    
    return(list(performance_predicted = performance_predicted, 
                performance_corrected = performance_corrected, 
                best_params = best_params, 
                model = model, 
                extended_model = extended_model, 
                test_data = saved_test_data))
  })
  
  return(outer_cv_results)
}


aggregate_results <- function(cv_results) {
  # Collect performance metrics from each fold
  performance_metrics_predicted <- do.call(rbind, lapply(cv_results, function(x) x$performance_predicted))
  performance_metrics_corrected <- do.call(rbind, lapply(cv_results, function(x) x$performance_corrected))
  
  # Collect best hyperparameters from each fold
  best_hyperparams <- do.call(rbind, lapply(cv_results, function(x) x$best_params))
  
  # Collect test data from each fold
  test_data_list <- lapply(cv_results, function(x) x$test_data)
  
  # Return a list with performance metrics, best hyperparameters, and test data
  return(list(performance_metrics_predicted = performance_metrics_predicted, performance_metrics_corrected = performance_metrics_corrected, best_hyperparams = best_hyperparams, test_data_list = test_data_list))
}


get_best_model <- function(cv_results, metric = "RMSE") {
  # Initialize variables to keep track of the best model and its performance
  best_performance <- Inf
  best_model <- NULL
  best_extended_model <- NULL
  best_test_data <- NULL
  best_params <- NULL
  
  # Iterate over each fold's results
  for (result in cv_results) {
    # Calculate the mean performance metric for the current fold
    performance_metric <- mean(result$performance_corrected[[metric]])
    
    # Check if the current model's performance is better than the best one found so far
    if (performance_metric < best_performance) {
      best_performance <- performance_metric
      best_model <- result$model
      best_extended_model <- result$extended_model
      best_test_data <- result$test_data
      best_params <- result$best_params
    }
  }
  
  return(list(best_model = best_model, best_extended_model = best_extended_model, best_performance = best_performance, best_test_data = best_test_data, best_params = best_params))
}


```



# Model Implementations
## Ridge Regression
```{r}

# Perform nested cross-validation for Ridge Regression
set.seed(18)
ridge_nested_cv <- nested_cv(trainData, "ridge", ridge_grid, inner_train_control, outer_train_control)

# Aggregate results
ridge_aggregate_results <- aggregate_results(ridge_nested_cv)

# Get Best Model
ridge_best <- get_best_model(ridge_nested_cv, metric = "RMSE")


# Save the ridge_nested_cv and ridge_aggregate_results objects to an RData file
save(ridge_nested_cv, ridge_best, file = paste0(root,"data/ridge_nested_cv_results.RData"))
```

# Graph Ridge
```{r}


# Assuming ridge_best$best_test_data contains the necessary data
test_data <- ridge_best$best_test_data

# Calculate adjusted R-squared for corrected brainage
model_corrected <- lm(corrected_brainage ~ p21022, data = test_data)
adj_r_squared_corrected <- summary(model_corrected)$adj.r.squared

# Calculate adjusted R-squared for uncorrected brainage
model_uncorrected <- lm(predicted_brainage ~ p21022, data = test_data)
adj_r_squared_uncorrected <- summary(model_uncorrected)$adj.r.squared

# Calculate MAE and RMSE for corrected brainage
mae_corrected <- mean(abs(test_data$corrected_brainage - test_data$p21022))
rmse_corrected <- sqrt(mean((test_data$corrected_brainage - test_data$p21022)^2))

# Calculate MAE and RMSE for uncorrected brainage
mae_uncorrected <- mean(abs(test_data$predicted_brainage - test_data$p21022))
rmse_uncorrected <- sqrt(mean((test_data$predicted_brainage - test_data$p21022)^2))

# Create annotations text for corrected brainage
annotation_text_corrected <- paste(
  "Corrected Brainage:\n",
  "Adj R-squared: ", round(adj_r_squared_corrected, 3), "\n",
  "MAE: ", round(mae_corrected, 2), "\n",
  "RMSE: ", round(rmse_corrected, 2), sep = ""
)

# Create annotations text for uncorrected brainage
annotation_text_uncorrected <- paste(
  "Uncorrected Brainage:\n",
  "Adj R-squared: ", round(adj_r_squared_uncorrected, 3), "\n",
  "MAE: ", round(mae_uncorrected, 2), "\n",
  "RMSE: ", round(rmse_uncorrected, 2), sep = ""
)

# Create scatterplot with annotations
ridge_brainage_plot <- ggplot(test_data, aes(x = p21022)) +
  geom_point(aes(y = corrected_brainage, color = "Corrected"), alpha = 0.5) +
  geom_point(aes(y = predicted_brainage, color = "Uncorrected"), alpha = 0.5) +
  geom_smooth(aes(y = corrected_brainage, color = "Corrected"), method = "lm", se = TRUE, linetype = "solid") +
  geom_smooth(aes(y = predicted_brainage, color = "Uncorrected"), method = "lm", se = TRUE, linetype = "solid") +
  geom_abline(slope = 1, intercept = 0, linetype = "dotted", color = "black") +
  labs(
    title = "Ridge",
    x = "Chronological Age",
    y = "Brain Age",
    color = "Type"
  ) +
  theme_minimal() +
  theme(
    plot.title = element_text(size = 20, face = "bold"),
    axis.title = element_text(size = 15),
    axis.text = element_text(size = 12)
  ) +
  scale_color_manual(values = c("Corrected" = "blue", "Uncorrected" = "red")) +
  annotate("text", x = -Inf, y = Inf, label = annotation_text_corrected, hjust = -0.1, 
           vjust = 1.1, size = 3, color = "blue", parse = FALSE) +
  annotate("text", x = -Inf, y = Inf, label = annotation_text_uncorrected, hjust = -0.1, 
           vjust = 2.1, size = 3, color = "red", parse = FALSE)

# Create scatterplot with annotations
ridge_brainagegap_plot <- ggplot(test_data, aes(x = p21022)) +
  geom_point(aes(y = corrected_brain_age_gap, color = "Corrected"), alpha = 0.5) +
  geom_point(aes(y = uncorrected_brain_age_gap, color = "Uncorrected"), alpha = 0.5) +
  geom_smooth(aes(y = corrected_brain_age_gap, color = "Corrected"), method = "lm", se = TRUE, linetype = "solid") +
  geom_smooth(aes(y = uncorrected_brain_age_gap, color = "Uncorrected"), method = "lm", se = TRUE, linetype = "solid") +
  geom_abline(slope = 0, intercept = 0, linetype = "dotted", color = "black") +
  labs(
    title = "Ridge",
    x = "Chronological Age",
    y = "Brain Age Gap",
    color = "Type"
  ) +
  theme_minimal() +
  theme(
    plot.title = element_text(size = 20, face = "bold"),
    axis.title = element_text(size = 15),
    axis.text = element_text(size = 12)
  ) +
  scale_color_manual(values = c("Corrected" = "blue", "Uncorrected" = "red"))


ggsave("ridge_brainage_plot.png", plot = ridge_brainage_plot, width = 10, height = 7)
ggsave("ridge_brainagegap_plot.png", plot = ridge_brainagegap_plot, width = 10, height = 7)
```

## Support Vector Regression (SVR)
NB: Takes a while to run
```{r}
set.seed(18)

svr_nested_cv <- nested_cv(trainData, "svmRadial", svr_grid, inner_train_control, outer_train_control)

# Aggregate results
svr_aggregate_results <- aggregate_results(svr_nested_cv)

# Get Best Model
svr_best <- get_best_model(svr_nested_cv, metric = "RMSE")

# Save the ridge_nested_cv and ridge_aggregate_results objects to an RData file
save(svr_nested_cv, svr_best, file = paste0(root,"data/svr_nested_cv_results.RData"))
```

# Graph SVR
```{r}

# Assuming ridge_best$best_test_data contains the necessary data
test_data <- svr_best$best_test_data

# Calculate adjusted R-squared for corrected brainage
model_corrected <- lm(corrected_brainage ~ p21022, data = test_data)
adj_r_squared_corrected <- summary(model_corrected)$adj.r.squared

# Calculate adjusted R-squared for uncorrected brainage
model_uncorrected <- lm(predicted_brainage ~ p21022, data = test_data)
adj_r_squared_uncorrected <- summary(model_uncorrected)$adj.r.squared

# Calculate MAE and RMSE for corrected brainage
mae_corrected <- mean(abs(test_data$corrected_brainage - test_data$p21022))
rmse_corrected <- sqrt(mean((test_data$corrected_brainage - test_data$p21022)^2))

# Calculate MAE and RMSE for uncorrected brainage
mae_uncorrected <- mean(abs(test_data$predicted_brainage - test_data$p21022))
rmse_uncorrected <- sqrt(mean((test_data$predicted_brainage - test_data$p21022)^2))

# Create annotations text for corrected brainage
annotation_text_corrected <- paste(
  "Corrected Brainage:\n",
  "Adj R-squared: ", round(adj_r_squared_corrected, 3), "\n",
  "MAE: ", round(mae_corrected, 2), "\n",
  "RMSE: ", round(rmse_corrected, 2), sep = ""
)

# Create annotations text for uncorrected brainage
annotation_text_uncorrected <- paste(
  "Uncorrected Brainage:\n",
  "Adj R-squared: ", round(adj_r_squared_uncorrected, 3), "\n",
  "MAE: ", round(mae_uncorrected, 2), "\n",
  "RMSE: ", round(rmse_uncorrected, 2), sep = ""
)

# Create scatterplot with annotations
svr_brainage_plot <- ggplot(test_data, aes(x = p21022)) +
  geom_point(aes(y = corrected_brainage, color = "Corrected"), alpha = 0.5) +
  geom_point(aes(y = predicted_brainage, color = "Uncorrected"), alpha = 0.5) +
  geom_smooth(aes(y = corrected_brainage, color = "Corrected"), method = "lm", se = TRUE, linetype = "solid") +
  geom_smooth(aes(y = predicted_brainage, color = "Uncorrected"), method = "lm", se = TRUE, linetype = "solid") +
  geom_abline(slope = 1, intercept = 0, linetype = "dotted", color = "black") +
  labs(
    title = "SVR",
    x = "Chronological Age",
    y = "Brain Age",
    color = "Type"
  ) +
  theme_minimal() +
  theme(
    plot.title = element_text(size = 20, face = "bold"),
    axis.title = element_text(size = 15),
    axis.text = element_text(size = 12)
  ) +
  scale_color_manual(values = c("Corrected" = "blue", "Uncorrected" = "red")) +
  annotate("text", x = -Inf, y = Inf, label = annotation_text_corrected, hjust = -0.1, 
           vjust = 1.1, size = 3, color = "blue", parse = FALSE) +
  annotate("text", x = -Inf, y = Inf, label = annotation_text_uncorrected, hjust = -0.1, 
           vjust = 2.1, size = 3, color = "red", parse = FALSE)


# Create scatterplot with annotations
svr_brainagegap_plot <- ggplot(test_data, aes(x = p21022)) +
  geom_point(aes(y = corrected_brain_age_gap, color = "Corrected"), alpha = 0.5) +
  geom_point(aes(y = uncorrected_brain_age_gap, color = "Uncorrected"), alpha = 0.5) +
  geom_smooth(aes(y = corrected_brain_age_gap, color = "Corrected"), method = "lm", se = TRUE, linetype = "solid") +
  geom_smooth(aes(y = uncorrected_brain_age_gap, color = "Uncorrected"), method = "lm", se = TRUE, linetype = "solid") +
  geom_abline(slope = 0, intercept = 0, linetype = "dotted", color = "black") +
  labs(
    title = "SVR",
    x = "Chronological Age",
    y = "Brain Age Gap",
    color = "Type"
  ) +
  theme_minimal() +
  theme(
    plot.title = element_text(size = 20, face = "bold"),
    axis.title = element_text(size = 15),
    axis.text = element_text(size = 12)
  ) +
  scale_color_manual(values = c("Corrected" = "blue", "Uncorrected" = "red"))

ggsave("svr_brainage_plot.png", plot = svr_brainage_plot, width = 10, height = 7)
ggsave("svr_brainagegap_plot.png", plot = svr_brainagegap_plot, width = 10, height = 7)
```



## Gaussian Process Regression (GPR)
```{r}

gpr_nested_cv <- nested_cv(trainData, "gaussprRadial", NULL, inner_train_control, outer_train_control)

# Aggregate results
gpr_aggregate_results <- aggregate_results(gpr_nested_cv)

# Get Best Model
gpr_best <- get_best_model(gpr_nested_cv, metric = "RMSE")

# Save the ridge_nested_cv and ridge_aggregate_results objects to an RData file
save(gpr_nested_cv, gpr_best, file = paste0(root,"data/gpr_nested_cv_results.RData"))

stopCluster(cl)
```

# Graph GPR
```{r}
# Assuming ridge_best$best_test_data contains the necessary data
test_data <- gpr_best$best_test_data

# Calculate adjusted R-squared for corrected brainage
model_corrected <- lm(corrected_brainage ~ p21022, data = test_data)
adj_r_squared_corrected <- summary(model_corrected)$adj.r.squared

# Calculate adjusted R-squared for uncorrected brainage
model_uncorrected <- lm(predicted_brainage ~ p21022, data = test_data)
adj_r_squared_uncorrected <- summary(model_uncorrected)$adj.r.squared

# Calculate MAE and RMSE for corrected brainage
mae_corrected <- mean(abs(test_data$corrected_brainage - test_data$p21022))
rmse_corrected <- sqrt(mean((test_data$corrected_brainage - test_data$p21022)^2))

# Calculate MAE and RMSE for uncorrected brainage
mae_uncorrected <- mean(abs(test_data$predicted_brainage - test_data$p21022))
rmse_uncorrected <- sqrt(mean((test_data$predicted_brainage - test_data$p21022)^2))

# Create annotations text for corrected brainage
annotation_text_corrected <- paste(
  "Corrected Brainage:\n",
  "Adj R-squared: ", round(adj_r_squared_corrected, 3), "\n",
  "MAE: ", round(mae_corrected, 2), "\n",
  "RMSE: ", round(rmse_corrected, 2), sep = ""
)

# Create annotations text for uncorrected brainage
annotation_text_uncorrected <- paste(
  "Uncorrected Brainage:\n",
  "Adj R-squared: ", round(adj_r_squared_uncorrected, 3), "\n",
  "MAE: ", round(mae_uncorrected, 2), "\n",
  "RMSE: ", round(rmse_uncorrected, 2), sep = ""
)

# Create scatterplot with annotations
gpr_brainage_plot <- ggplot(test_data, aes(x = p21022)) +
  geom_point(aes(y = corrected_brainage, color = "Corrected"), alpha = 0.5) +
  geom_point(aes(y = predicted_brainage, color = "Uncorrected"), alpha = 0.5) +
  geom_smooth(aes(y = corrected_brainage, color = "Corrected"), method = "lm", se = TRUE, linetype = "solid") +
  geom_smooth(aes(y = predicted_brainage, color = "Uncorrected"), method = "lm", se = TRUE, linetype = "solid") +
  geom_abline(slope = 1, intercept = 0, linetype = "dotted", color = "black") +
  labs(
    title = "GPR",
    x = "Chronological Age",
    y = "Brain Age",
    color = "Type"
  ) +
  theme_minimal() +
  theme(
    plot.title = element_text(size = 20, face = "bold"),
    axis.title = element_text(size = 15),
    axis.text = element_text(size = 12)
  ) +
  scale_color_manual(values = c("Corrected" = "blue", "Uncorrected" = "red")) +
  annotate("text", x = -Inf, y = Inf, label = annotation_text_corrected, hjust = -0.1, 
           vjust = 1.1, size = 3, color = "blue", parse = FALSE) +
  annotate("text", x = -Inf, y = Inf, label = annotation_text_uncorrected, hjust = -0.1, 
           vjust = 2.1, size = 3, color = "red", parse = FALSE)



# Create scatterplot with annotations
gpr_brainagegap_plot <- ggplot(test_data, aes(x = p21022)) +
  geom_point(aes(y = corrected_brain_age_gap, color = "Corrected"), alpha = 0.5) +
  geom_point(aes(y = uncorrected_brain_age_gap, color = "Uncorrected"), alpha = 0.5) +
  geom_smooth(aes(y = corrected_brain_age_gap, color = "Corrected"), method = "lm", se = TRUE, linetype = "solid") +
  geom_smooth(aes(y = uncorrected_brain_age_gap, color = "Uncorrected"), method = "lm", se = TRUE, linetype = "solid") +
  geom_abline(slope = 0, intercept = 0, linetype = "dotted", color = "black") +
  labs(
    title = "GPR",
    x = "Chronological Age",
    y = "Brain Age Gap",
    color = "Type"
  ) +
  theme_minimal() +
  theme(
    plot.title = element_text(size = 20, face = "bold"),
    axis.title = element_text(size = 15),
    axis.text = element_text(size = 12)
  ) +
  scale_color_manual(values = c("Corrected" = "blue", "Uncorrected" = "red"))

ggsave("gpr_brainage_plot.png", plot = gpr_brainage_plot, width = 10, height = 7)
ggsave("gpr_brainagegap_plot.png", plot = gpr_brainagegap_plot, width = 10, height = 7)
```



```{r}

# Arrange the plots in a grid
grid.arrange(
  ridge_brainage_plot, svr_brainage_plot, gpr_brainage_plot,
  ridge_brainagegap_plot, svr_brainagegap_plot, gpr_brainagegap_plot,
  ncol = 3, nrow = 2
)

# Save the combined plot as a PNG file
combined_plot <- grid.arrange(
  ridge_brainage_plot, svr_brainage_plot, gpr_brainage_plot,
  ridge_brainagegap_plot, svr_brainagegap_plot, gpr_brainagegap_plot,
  ncol = 3, nrow = 2
)

# Add a single title
title <- textGrob("Predicted Brain Age and Brain Age Gap for Healthy Participants", 
                  gp = gpar(fontsize = 30, fontface = "bold"))

# Combine the title and the grid of plots
final_plot <- grid.arrange(title, combined_plot, ncol = 1, heights = c(0.1, 1))

# Save the combined plot as a PNG file
ggsave("combined_brainage_plots.png", plot = final_plot, width = 15, height = 10)

```












