---
title: "HealthyUnhealthySplit"
output: html_document
date: "2024-05-28"
---

This file separates all participants who are healthy and unhealthy. Meant to be merged with 
brain age and bio age participants.

# Source and read in data
```{r}
source("init.r")
healthy_unhealthy_final <- read.csv(paste0(root, "data/Healthy_Unhealthy_final.csv"))
healthy_unhealthy_Age <- read.csv(paste0(root, "data/Healthy_Unhealthy_Age.csv"))

healthy_unhealthy <- merge(healthy_unhealthy_final, 
                           healthy_unhealthy_Age %>% dplyr::select(eid, p21003_i0:p21003_i3),
                           by = "eid")

skim(healthy_unhealthy)
```

codebook:
eid - Participant ID
p20008_i3_a14 - non-cancer illness instance 3
p134_i0 - self-reported cancers instance 0
p134_i1 - self-reported cancers instance 1
p134_i2 - self-reported cancers instance 2
p134_i3 - self-reported cancers instance 3
p135_i0 - non-cancer illnesses instance 0
p135_i1 - non-cancer illnesses instance 1
p135_i2 - non-cancer illnesses instance 2 
p135_i3 - non-cancer illnesses instance 3 
p31 - Sex

# Find all healthy at instance 1
Should have had no cases at any instance before instance 1 as well
```{r}
skim(healthy_unhealthy$p134_i1) # Complete rate is very low for instance 1

healthy_unhealthy
# Healthy at instance 0
healthy_0 <- healthy_unhealthy %>% 
  dplyr::filter(p134_i0 == 0 & p135_i0 == 0)

# unhealthy at instance 0 
unhealthy_0 <- healthy_unhealthy %>% 
  dplyr::filter(p134_i0 > 0 | p135_i0 > 0)

nrow(healthy_0) # 117620
nrow(unhealthy_0) # 383881
```

More are unhealthy than healthy. 







